\documentclass[11pt,a4paper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage{array}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\hypersetup{
    colorlinks=true,
    linkcolor=brandred,
    urlcolor=brandred
}

\definecolor{brandred}{HTML}{720101}
\definecolor{brandgold}{HTML}{A66A00}
\definecolor{softgray}{HTML}{F7F3EC}
\definecolor{darktext}{HTML}{111827}

\pagestyle{fancy}
\fancyhf{}
\lhead{\textbf{Eloquente Catering Event Catering System}}
\rhead{\textbf{Rated FRD}}
\cfoot{\thepage}

\titleformat{\section}
  {\Large\bfseries\color{brandred}}
  {\thesection}{0.7em}{}

\titleformat{\subsection}
  {\large\bfseries\color{brandgold}}
  {\thesubsection}{0.7em}{}

\renewcommand{\arraystretch}{1.35}
\setlength{\tabcolsep}{5pt}
\setlist[itemize]{leftmargin=1.2em}

\newcolumntype{L}[1]{>{\raggedright\arraybackslash}p{#1}}
\newcolumntype{C}[1]{>{\centering\arraybackslash}p{#1}}

\newcommand{\statusdone}{\textbf{[x]}}
\newcommand{\statuspartial}{\textbf{[{\textasciitilde}]}}
\newcommand{\statusmissing}{\textbf{[ ]}}
\newcommand{\statusrisk}{\textbf{[!]}}

\begin{document}

\begin{titlepage}
    \centering
    \vspace*{1.5cm}
    {\Huge\bfseries\color{brandred} Rated Functional Requirements Document \par}
    \vspace{0.5cm}
    {\Large Eloquente Catering Event Catering System \par}
    \vspace{1.5cm}
    \begin{tabular}{rl}
        \textbf{Date:} & 2026-05-25 \\
        \textbf{Prepared for:} & Development team, project evaluators, and business stakeholders \\
        \textbf{Basis:} & Current implemented system, FRD, rating review, and error review \\
    \end{tabular}
    \vfill
    {\large Functional readiness: \textbf{78 / 100}\par}
    {\large Production readiness: \textbf{70 / 100}\par}
    {\large Demonstration readiness: \textbf{89 / 100}\par}
\end{titlepage}

\tableofcontents
\newpage

\section{Rating Legend}

\begin{longtable}{L{0.15\textwidth} L{0.55\textwidth} C{0.20\textwidth}}
\toprule
\textbf{Mark} & \textbf{Meaning} & \textbf{Completion Range} \\
\midrule
\statusdone & Mostly complete and usable & 85--100\% \\
\statuspartial & Partially complete or needs polishing & 50--84\% \\
\statusmissing & Not implemented or not reliable enough & 0--49\% \\
\statusrisk & Implemented but risky or needs urgent correction & Any percent \\
\bottomrule
\end{longtable}

\section{Overall Functional Completion}

\begin{center}
    \fcolorbox{brandred}{softgray}{
        \begin{minipage}{0.88\textwidth}
            \centering
            \vspace{0.3cm}
            {\Large\textbf{Estimated Functional Completion: 78 / 100}}\\[0.2cm]
            The system has most major modules implemented, but several workflows still need final hardening before real production use.
            The most urgent concern is the legacy manual payment verification path, which can still mark payments as verified from a customer-facing route.
            \vspace{0.3cm}
        \end{minipage}
    }
\end{center}

\section{Summary By Module}

\begin{longtable}{L{0.20\textwidth} C{0.10\textwidth} C{0.12\textwidth} C{0.13\textwidth} L{0.35\textwidth}}
\toprule
\textbf{Module} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Module} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
\endhead
Public website & \statusdone & 88\% & 8.6/10 & Public pages work. Not 100\% because final content governance, availability-driven notices, and production copy review are still needed. \\
Authentication and profile & \statuspartial & 84\% & 8.2/10 & Login, registration, and profile work with stronger staff detail fields. Not 100\% because final security review, staff profile polish, and stronger account recovery flows are still needed. \\
Customer booking & \statusdone & 87\% & 8.5/10 & Booking wizard is strong and now has stronger availability override support. Not 100\% because edge cases, budget generator accuracy, and customer-friendly validation errors still need cleanup. \\
Customer dashboard & \statuspartial & 80\% & 7.8/10 & Dashboard is useful. Not 100\% because booking/payment status labels and refund/payment edge states still need standardization. \\
Payments & \statusrisk & 68\% & 6.4/10 & PayMongo exists. Not 100\% because the legacy manual payment route can still mark payments verified and must be removed or converted to proof review. \\
Marketing workflow & \statuspartial & 77\% & 7.5/10 & Intake workflow exists and availability visibility improved. Not 100\% because clarification still uses a browser prompt, queue priority can improve, and chat should connect better to booking review. \\
Food tasting & \statuspartial & 70\% & 7.0/10 & Tasting requests exist. Not 100\% because staff still need a tasting queue/calendar, confirmation flow, and outcome notes. \\
Accounting & \statuspartial & 70\% & 7.0/10 & Core accounting works. Not 100\% because PayMongo reconciliation, payment exception handling, and refund case records are still incomplete. \\
Admin & \statuspartial & 78\% & 7.7/10 & Admin is broad and now includes date availability controls. Not 100\% because some screens are dense, some labels are technical, and advanced configuration needs better separation. \\
Announcement CMS & \statusdone & 82\% & 8.0/10 & CMS foundation is strong. Not 100\% because approval workflow, content calendar, and stronger email scheduling controls are missing. \\
Chat and notifications & \statuspartial & 76\% & 7.5/10 & Chat and notifications work with better lazy-loading and richer user summaries. Not 100\% because staff chat still uses native dialogs and needs better booking context integration. \\
Reports and analytics & \statuspartial & 72\% & 7.2/10 & Reports are useful. Not 100\% because role-specific presets, action recommendations, export audit, and production data testing remain. \\
Data and business rules & \statuspartial & 78\% & 7.8/10 & Core records exist, including date availability override records. Not 100\% because refund cases, event preparation tasks, payment events, and feedback records are not fully modeled. \\
Non-functional requirements & \statuspartial & 74\% & 7.3/10 & Performance and security improved through lazy chart/chat loading and PHP config cleanup. Not 100\% because production hardening, broader tests, centralized statuses, and polished error handling remain. \\
\bottomrule
\end{longtable}

\section{Public Website Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
\endhead
FR-PUB-001 & Home Page & \statusdone & 90\% & 8.8/10 & Home page exists. To reach 100\%, add stronger availability-driven prompts, final copy review, and production image/content audit. \\
FR-PUB-002 & Menu Page & \statusdone & 88\% & 8.5/10 & Menu display works. To reach 100\%, finish image consistency, hide unavailable items perfectly, and test filtering with full production data. \\
FR-PUB-003 & Amenities Page & \statusdone & 86\% & 8.3/10 & Amenities page exists. To reach 100\%, connect amenities more tightly to event/package configuration and keep content editable/governed. \\
FR-PUB-004 & Contact Page & \statusdone & 86\% & 8.3/10 & Contact page exists. To reach 100\%, add clearer support routing by concern type and ensure active booking inquiries always route to chat. \\
FR-PUB-005 & Public Announcements & \statusdone & 82\% & 8.0/10 & Public announcements work. To reach 100\%, add approval, scheduling calendar, and stronger audience/publish safeguards. \\
\bottomrule
\end{longtable}

\section{Authentication And Profile Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-AUTH-001 & Registration & \statusdone & 86\% & 8.4/10 & Registration exists. To reach 100\%, add stronger account recovery, clearer validation copy, and final security checks for duplicate/invalid inputs. \\
FR-AUTH-002 & Login & \statusdone & 88\% & 8.5/10 & Login works. To reach 100\%, complete final session/security review and improve all failed-login and role-redirect edge states. \\
FR-AUTH-003 & Logout & \statusdone & 90\% & 8.8/10 & Logout works. To reach 100\%, test session invalidation across all role dashboards and browser back-button cases. \\
FR-AUTH-004 & Profile Management & \statuspartial & 82\% & 8.0/10 & Profile management exists with stronger staff detail fields. To reach 100\%, polish staff/admin profile UI, add clearer password rules, and audit profile update permissions. \\
\bottomrule
\end{longtable}

\section{Customer Booking Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
\endhead
FR-BOOK-001 & Start Booking & \statusdone & 90\% & 8.8/10 & Booking wizard is accessible. To reach 100\%, add server-side draft recovery and more abandonment recovery behavior. \\
FR-BOOK-002 & Select Event Type & \statusdone & 88\% & 8.5/10 & Event type selection works. To reach 100\%, sync event type setup/inclusions with admin-managed content and test all event types. \\
FR-BOOK-003 & Select Date And Time & \statusdone & 88\% & 8.5/10 & Calendar availability works with staff-managed overrides for blocked or limited dates. To reach 100\%, add stronger race-condition protection, full capacity testing, and clearer blocked-date explanations. \\
FR-BOOK-004 & Enter Guest Count & \statusdone & 86\% & 8.3/10 & Headcount and dietary notes exist. To reach 100\%, better validate unusual pax values and connect dietary notes to staff preparation views. \\
FR-BOOK-005 & Choose Package Method & \statusdone & 88\% & 8.5/10 & Three methods exist. To reach 100\%, test every back/forward path and preserve selections perfectly across method changes. \\
FR-BOOK-006 & Select Curated Package & \statusdone & 84\% & 8.1/10 & Curated packages work. To reach 100\%, reduce remaining text density, finish responsive states, and verify package data completeness. \\
FR-BOOK-007 & Build Menu & \statusdone & 86\% & 8.4/10 & Menu builder works. To reach 100\%, harden category minimums, empty states, filters, pagination, and selected-price calculations. \\
FR-BOOK-008 & Budget-Based Menu & \statuspartial & 72\% & 6.9/10 & Budget build exists. To reach 100\%, fix minimum budget calculation so it only promises full category coverage when it can generate it. \\
FR-BOOK-009 & Contact And Venue Details & \statusdone & 84\% & 8.0/10 & Venue details work. To reach 100\%, make logistics fees transparent and connect venue risks to staff operations checklist. \\
FR-BOOK-010 & Food Tasting Preference & \statusdone & 84\% & 8.1/10 & Tasting step exists. To reach 100\%, connect it to a staff tasting queue/calendar and enforce tasting slot availability. \\
FR-BOOK-011 & Final Review Modal & \statusdone & 86\% & 8.3/10 & Review modal exists. To reach 100\%, add cleaner validation summaries and edit shortcuts to the exact relevant step. \\
FR-BOOK-012 & Submit Booking & \statusdone & 86\% & 8.4/10 & Booking creation works. To reach 100\%, add broader tests for all package/payment/tasting combinations and friendlier validation mapping. \\
FR-BOOK-013 & Booking Updates & \statuspartial & 76\% & 7.4/10 & Updates exist. To reach 100\%, test every lock rule and show clearer explanations when edits are no longer allowed. \\
FR-BOOK-014 & Booking Cancellation & \statuspartial & 74\% & 7.2/10 & Cancellation exists. To reach 100\%, add refund case tracking, cancellation reasons, and clearer customer refund status. \\
\bottomrule
\end{longtable}

\section{Customer Dashboard Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-CDASH-001 & Dashboard Overview & \statusdone & 84\% & 8.1/10 & Dashboard works. To reach 100\%, simplify dense sections, standardize status displays, and test multiple active/history bookings. \\
FR-CDASH-002 & Customer Next Actions & \statuspartial & 80\% & 7.8/10 & Next actions exist. To reach 100\%, make one primary next action obvious for every booking/payment/refund state. \\
FR-CDASH-003 & Respond To Staff Request & \statusdone & 86\% & 8.4/10 & Clarification response works. To reach 100\%, add better notification timing, response history, and staff/customer read status. \\
FR-CDASH-004 & Payment Summary & \statuspartial & 78\% & 7.5/10 & Payment summary works. To reach 100\%, unify payment labels, remove raw statuses, and harden rush/partial/refund cases. \\
\bottomrule
\end{longtable}

\section{Payment Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-PAY-001 & Payment Schedule Generation & \statusdone & 84\% & 8.0/10 & Schedule generation exists. To reach 100\%, add regression tests for standard, rush 1, rush 2, discounts, and edited terms. \\
FR-PAY-002 & PayMongo Checkout & \statusdone & 82\% & 8.0/10 & PayMongo checkout exists. To reach 100\%, test all supported methods, expired sessions, retries, and webhook/local sync behavior. \\
FR-PAY-003 & PayMongo Webhook & \statusdone & 80\% & 7.8/10 & Webhook works. To reach 100\%, add event ID tracking, duplicate event handling proof, and reconciliation dashboard visibility. \\
FR-PAY-004 & Payment Verification & \statuspartial & 76\% & 7.3/10 & Verification exists. To reach 100\%, separate online paid, manually reviewed, rejected, expired, and overdue statuses clearly. \\
FR-PAY-005 & Manual Payment Safety & \statusrisk & 35\% & 3.5/10 & Not complete because old customer route can verify payments. To complete, remove or lock it and replace with proof upload pending Accounting review. \\
\bottomrule
\end{longtable}

\section{Marketing Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-MKT-001 & Booking Intake Queue & \statuspartial & 78\% & 7.6/10 & Intake queue exists. To reach 100\%, add priority sorting, SLA timers, stronger filters, and unresolved-message visibility. \\
FR-MKT-002 & Claim Booking & \statusdone & 88\% & 8.5/10 & Claiming works. To reach 100\%, add reassignment, assignment history, and admin override notes. \\
FR-MKT-003 & Review Checklist & \statusdone & 84\% & 8.1/10 & Checklist works. To reach 100\%, make checklist templates configurable and block approval when critical tasks are unfinished. \\
FR-MKT-004 & Request Customer Details & \statuspartial & 72\% & 6.8/10 & Flow works. To reach 100\%, replace browser prompt with branded modal, request templates, and clearer response tracking. \\
FR-MKT-005 & Approve Or Decline Booking & \statuspartial & 78\% & 7.5/10 & Status updates work. To reach 100\%, add decline reasons, approval side-effect checks, and clearer customer-facing result messages. \\
FR-MKT-006 & Live Event Status & \statuspartial & 74\% & 7.2/10 & Live status exists. To reach 100\%, add event preparation board, readiness gates, and event-day issue logging. \\
FR-MKT-007 & Availability Review & \statuspartial & 78\% & 7.6/10 & Marketing can view availability context. To reach 100\%, connect availability changes to booking review recommendations and show conflict warnings directly in queues. \\
\bottomrule
\end{longtable}

\section{Food Tasting Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-TASTE-001 & Submit Tasting Request & \statusdone & 84\% & 8.1/10 & Tasting request exists. To reach 100\%, validate tasting slot capacity and connect requests directly to staff scheduling. \\
FR-TASTE-002 & Manage Tasting Request & \statuspartial & 76\% & 7.4/10 & Customer management exists. To reach 100\%, add staff confirmation, reschedule flow, tasting outcome notes, and calendar conflict checks. \\
\bottomrule
\end{longtable}

\section{Accounting Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-ACC-001 & Payment Verification Tab & \statusdone & 82\% & 8.0/10 & Verification tab exists. To reach 100\%, add payment exception states and clearer PayMongo/local mismatch indicators. \\
FR-ACC-002 & Ledger & \statusdone & 80\% & 7.8/10 & Ledger exists. To reach 100\%, add stronger export options, audit trail, and filters for tax/refund/method reporting. \\
FR-ACC-003 & Payment Reminders & \statuspartial & 76\% & 7.4/10 & Manual reminders exist. To reach 100\%, add scheduled reminders before due date, on due date, and after overdue. \\
FR-ACC-004 & Payment Term Editing & \statusdone & 82\% & 8.0/10 & Payment terms can be edited. To reach 100\%, add approval rules for sensitive edits and clearer change history. \\
FR-ACC-005 & Refund Queue & \statuspartial & 76\% & 7.4/10 & Refund queue exists. To reach 100\%, create first-class refund cases with statuses, reason, approvals, and timeline. \\
FR-ACC-006 & Refund Processing & \statuspartial & 72\% & 7.0/10 & PayMongo refunds exist. To reach 100\%, improve non-technical errors, retry handling, and manual fallback tracking. \\
\bottomrule
\end{longtable}

\section{Admin Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-ADM-001 & Staff Account Management & \statusdone & 84\% & 8.1/10 & Staff management exists. To reach 100\%, add role-change audit, account status controls, and safer deletion/deactivation flow. \\
FR-ADM-002 & Customer Account Management & \statusdone & 82\% & 7.9/10 & Customer management exists. To reach 100\%, add customer profile history, deactivation instead of deletion, and clearer data impact warnings. \\
FR-ADM-003 & Booking Management & \statuspartial & 78\% & 7.5/10 & Booking management exists. To reach 100\%, standardize status wording, remove technical labels, and align with Marketing review workflow. \\
FR-ADM-004 & Menu Management & \statusdone & 84\% & 8.1/10 & Menu CRUD exists. To reach 100\%, add bulk edit/import, image validation, and change approval for customer-facing edits. \\
FR-ADM-005 & Package And Event Type Management & \statusdone & 82\% & 8.0/10 & Package/event config exists. To reach 100\%, hide advanced fields and add preview/approval before publishing. \\
FR-ADM-006 & Pricing Overrides & \statusdone & 82\% & 8.0/10 & Pricing overrides exist. To reach 100\%, add approval thresholds, history, and warnings for affected bookings. \\
FR-ADM-007 & Audit Logs & \statuspartial & 78\% & 7.5/10 & Audit logs exist. To reach 100\%, expand coverage to all sensitive actions and add better filtering/export. \\
FR-ADM-008 & Availability Controls & \statusdone & 84\% & 8.1/10 & Admin can manage date availability overrides for event slots and pax limits. To reach 100\%, add stronger audit history, conflict warnings, and confirmation before locking dates with existing interest. \\
\bottomrule
\end{longtable}

\section{Announcement CMS Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-CMS-001 & Create Announcement & \statusdone & 88\% & 8.5/10 & Creation exists. To reach 100\%, add content approval states, reusable templates, and stronger preview before publishing. \\
FR-CMS-002 & Publish Announcement & \statusdone & 86\% & 8.3/10 & Publishing exists. To reach 100\%, add scheduled publish windows, approval gates, and publish audit details. \\
FR-CMS-003 & Archive Announcement & \statusdone & 86\% & 8.3/10 & Archiving exists. To reach 100\%, add restore/unarchive flow and clearer archive reason tracking. \\
FR-CMS-004 & Email Announcement & \statuspartial & 78\% & 7.5/10 & Email support exists. To reach 100\%, add delivery tracking, unsubscribe/compliance handling, and scheduled campaign sending. \\
\bottomrule
\end{longtable}

\section{Chat, Notifications, Reports, Data, And Non-Functional Requirements}

\subsection{Chat And Messaging}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-CHAT-001 & Customer Chat & \statusdone & 84\% & 8.2/10 & Customer chat exists and lazy-loading reduces initial page cost. To reach 100\%, attach booking context clearly and improve offline/loading/error states. \\
FR-CHAT-002 & Staff Chat Inbox & \statuspartial & 76\% & 7.4/10 & Staff chat exists. To reach 100\%, remove native dialogs, improve transfer/claim UX, and connect conversations to booking review. \\
FR-CHAT-003 & Realtime Or Refresh Behavior & \statuspartial & 76\% & 7.4/10 & Refresh behavior and repeated opening improved through cached/lazy chat loading. To reach 100\%, benchmark repeated open/close, add reliable realtime fallback, and avoid repeated slow fetches. \\
\bottomrule
\end{longtable}

\subsection{Notifications}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-NOTIF-001 & Notification Bell & \statusdone & 84\% & 8.2/10 & Notification bell exists with richer user summary support. To reach 100\%, add better grouping, action links, and complete read-state consistency. \\
FR-NOTIF-002 & Booking Status Notifications & \statuspartial & 78\% & 7.5/10 & Booking notifications exist. To reach 100\%, centralize status wording and notify every major workflow transition correctly. \\
FR-NOTIF-003 & Payment Notifications & \statuspartial & 76\% & 7.4/10 & Payment notifications exist. To reach 100\%, automate due/overdue reminders and improve PayMongo confirmation messaging. \\
\bottomrule
\end{longtable}

\subsection{Reports And Analytics}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
FR-REP-001 & Analytics Dashboard & \statuspartial & 74\% & 7.2/10 & Analytics exist. To reach 100\%, test with production-scale data and add clearer action recommendations per insight. \\
FR-REP-002 & Report Builder & \statusdone & 82\% & 8.0/10 & Builder exists. To reach 100\%, add more role-specific blocks, stronger drag/drop polish, and better responsive behavior. \\
FR-REP-003 & Saved Reports & \statusdone & 82\% & 8.0/10 & Saved reports exist. To reach 100\%, add ownership/permissions, version history, and duplicate/share actions. \\
FR-REP-004 & Report Export & \statuspartial & 76\% & 7.4/10 & Export exists. To reach 100\%, add export audit trail, cleaner PDF layout, and business-ready spreadsheet formatting. \\
\bottomrule
\end{longtable}

\subsection{Data Requirements}

\begin{longtable}{L{0.24\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.36\textwidth}}
\toprule
\textbf{Data Entity} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
\endfirsthead
\toprule
\textbf{Data Entity} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
\endhead
Users & \statusdone & 88\% & 8.5/10 & Implemented. To reach 100\%, add deactivation/status history, stronger profile fields, and complete audit for account changes. \\
Bookings & \statusdone & 88\% & 8.5/10 & Implemented with workflow fields. To reach 100\%, add full lifecycle states for preparation, completion, feedback, and adjustments. \\
Booking review tasks & \statusdone & 84\% & 8.1/10 & Implemented. To reach 100\%, add configurable templates, due dates, assignment history, and required task enforcement. \\
Payments & \statuspartial & 78\% & 7.5/10 & Implemented. To reach 100\%, remove manual self-verification risk and add payment event/reconciliation records. \\
Food tastings & \statuspartial & 76\% & 7.4/10 & Implemented. To reach 100\%, add tasting queue/calendar, confirmation statuses, and outcome records. \\
Messages/conversations & \statuspartial & 76\% & 7.4/10 & Implemented. To reach 100\%, polish UX, remove native dialogs, and attach conversations to bookings. \\
Notifications & \statusdone & 82\% & 8.0/10 & Implemented. To reach 100\%, add better categories, action links, and full transition coverage. \\
Menu items & \statusdone & 86\% & 8.3/10 & Implemented. To reach 100\%, add image management, availability scheduling, and bulk/approval tools. \\
Packages & \statusdone & 84\% & 8.1/10 & Implemented. To reach 100\%, add versioning, preview, and approval before customer-facing changes go live. \\
Event types & \statusdone & 84\% & 8.1/10 & Implemented. To reach 100\%, add stronger setup governance and preview effects on booking. \\
Announcements & \statusdone & 84\% & 8.1/10 & Implemented. To reach 100\%, add approval, publishing calendar, delivery tracking, and audit history. \\
Report templates/runs & \statusdone & 82\% & 8.0/10 & Implemented. To reach 100\%, add sharing/permissions, export audit, and version history. \\
Audit logs & \statuspartial & 78\% & 7.5/10 & Implemented. To reach 100\%, cover every sensitive action and add filtering/export. \\
Pricing overrides & \statusdone & 82\% & 8.0/10 & Implemented. To reach 100\%, add approval thresholds, change impact preview, and full history. \\
Calendar availability overrides & \statusdone & 84\% & 8.1/10 & Implemented with staff-managed date locks and capacity limits. To reach 100\%, add full audit history, conflict warnings, and bulk/recurring override tools. \\
Refund cases & \statusmissing & 25\% & 2.5/10 & Refunds are actions, not full case records. To complete, add statuses, approvals, reason, timeline, and provider response tracking. \\
Event preparation tasks & \statusmissing & 20\% & 2.0/10 & Event preparation is not fully modeled. To complete, add operations board, checklist tasks, assignees, and event sheet export. \\
Feedback requests/responses & \statusmissing & 20\% & 2.0/10 & Post-event feedback is mostly future work. To complete, add feedback links, ratings, low-rating alerts, and testimonial approval. \\
\bottomrule
\end{longtable}

\subsection{Business Rules}

\begin{longtable}{L{0.24\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.36\textwidth}}
\toprule
\textbf{Rule Area} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
Booking ownership & \statusdone & 90\% & 8.8/10 & Authenticated ownership is enforced. To reach 100\%, add tests proving users cannot access or modify others' bookings. \\
Date availability & \statusdone & 88\% & 8.5/10 & Availability checks and staff override controls exist. To reach 100\%, add concurrency protection, audit history, and stress tests for simultaneous bookings. \\
Guest minimums & \statusdone & 84\% & 8.1/10 & Guest rules exist. To reach 100\%, centralize all pax limits and validate every package/event type combination. \\
Server-side pricing validation & \statuspartial & 78\% & 7.5/10 & Validation exists. To reach 100\%, make budget and package/menu pricing fully server-verified with clear mismatch handling. \\
Payment step sequencing & \statusdone & 82\% & 8.0/10 & Sequencing exists. To reach 100\%, add regression tests for edited terms, rush bookings, failed payments, and retries. \\
Customer cannot self-verify payments & \statusrisk & 35\% & 3.5/10 & Not complete because \texttt{/api/bookings/pay} remains reachable. Remove or lock it and route manual proof to Accounting review. \\
Refund policy & \statuspartial & 72\% & 7.0/10 & Refund calculation exists. To reach 100\%, add refund cases, approval thresholds, customer status, and policy display. \\
Role access & \statuspartial & 80\% & 7.8/10 & Role middleware exists. To reach 100\%, audit every endpoint/action and add tests for unauthorized role access. \\
\bottomrule
\end{longtable}

\subsection{Non-Functional Requirements}

\begin{longtable}{L{0.15\textwidth} L{0.22\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.25\textwidth}}
\toprule
\textbf{ID} & \textbf{Requirement} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
NFR-001 & Security & \statuspartial & 72\% & 7.0/10 & Improved. To reach 100\%, remove payment self-verification, harden environment settings, audit roles, and add security tests. \\
NFR-002 & Performance & \statusdone & 82\% & 8.1/10 & Optimizations now include lazy chart loading, deferred chat loading, and PHP config cleanup. To reach 100\%, benchmark large datasets, chat open/close cycles, analytics queries, and production builds. \\
NFR-003 & Usability & \statuspartial & 73\% & 7.1/10 & Customer UX is strong. To reach 100\%, simplify staff dashboards, remove native dialogs, and standardize UI patterns. \\
NFR-004 & Reliability & \statuspartial & 72\% & 7.1/10 & Core flows work. To reach 100\%, add feature tests, webhook idempotency proof, retry handling, and failure recovery paths. \\
NFR-005 & Maintainability & \statuspartial & 74\% & 7.2/10 & Structure improved. To reach 100\%, centralize status mappers, modal components, filter components, and business rules. \\
\bottomrule
\end{longtable}

\subsection{Integration Requirements}

\begin{longtable}{L{0.24\textwidth} C{0.08\textwidth} C{0.10\textwidth} C{0.10\textwidth} L{0.36\textwidth}}
\toprule
\textbf{Integration} & \textbf{Status} & \textbf{Completion} & \textbf{Rating} & \textbf{Notes} \\
\midrule
PayMongo checkout & \statusdone & 82\% & 8.0/10 & Implemented. To reach 100\%, test every checkout state, expired sessions, retries, and production webhook deployment setup. \\
PayMongo webhook & \statusdone & 80\% & 7.8/10 & Implemented with validation. To reach 100\%, store webhook event IDs, expose reconciliation state, and prove duplicate safety. \\
PayMongo refund & \statuspartial & 72\% & 7.0/10 & Implemented. To reach 100\%, add refund case records, staff-friendly errors, retry tracking, and admin approval thresholds. \\
Email notifications & \statuspartial & 76\% & 7.4/10 & Implemented in key areas. To reach 100\%, add templates, scheduled reminders, delivery logs, and complete event coverage. \\
\bottomrule
\end{longtable}

\section{Requirements Needing Immediate Attention}

\begin{longtable}{C{0.10\textwidth} L{0.34\textwidth} L{0.42\textwidth}}
\toprule
\textbf{Priority} & \textbf{Requirement} & \textbf{Reason} \\
\midrule
1 & FR-PAY-005 Manual Payment Safety & Customers must not be able to mark payments verified. \\
2 & FR-BOOK-008 Budget-Based Menu & Helper text must not promise full category coverage unless it can generate it. \\
3 & FR-MKT-004 Request Customer Details & Browser prompt should be replaced by a branded modal. \\
4 & FR-CDASH-004 Payment Summary & Payment labels and edge cases must be consistent. \\
5 & FR-ADM-003 Booking Management & Admin wording/status display should be business-friendly. \\
6 & FR-ACC-006 Refund Processing & Refund errors and tracking need better staff-facing workflow. \\
7 & NFR-001 Security & Production hardening is still needed. \\
8 & NFR-003 Usability & Native alerts/confirms should be removed from major workflows. \\
\bottomrule
\end{longtable}

\section{Final Rating}

\begin{center}
    \begin{tabular}{L{0.45\textwidth} C{0.25\textwidth}}
    \toprule
    \textbf{Readiness Area} & \textbf{Score} \\
    \midrule
    Functional readiness & 78 / 100 \\
    Production readiness & 70 / 100 \\
    Demonstration readiness & 89 / 100 \\
    \bottomrule
    \end{tabular}
\end{center}

\vspace{0.5cm}
\noindent
The system is impressive and feature-rich, but the final stretch should focus on safety, consistency, and operational polish rather than adding many new features.

\end{document}
