\documentclass[11pt,a4paper]{article}

\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage{array}
\usepackage{amssymb}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{hyperref}
\usepackage{titlesec}

\definecolor{eloMaroon}{HTML}{8B0000}
\definecolor{eloGold}{HTML}{A56600}
\definecolor{eloInk}{HTML}{07142F}
\definecolor{eloMuted}{HTML}{5F7188}
\definecolor{eloPaper}{HTML}{FBF8F2}

\hypersetup{
  colorlinks=true,
  linkcolor=eloMaroon,
  urlcolor=eloMaroon,
  pdftitle={Trial 1 End-to-End System Test Script},
  pdfauthor={Eloquente Catering System QA}
}

\pagestyle{fancy}
\fancyhf{}
\lhead{\textcolor{eloMaroon}{Eloquente Catering System}}
\rhead{Trial 1 QA Script}
\cfoot{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

\titleformat{\section}
  {\Large\bfseries\color{eloMaroon}}
  {\thesection}{0.75em}{}

\titleformat{\subsection}
  {\large\bfseries\color{eloInk}}
  {\thesubsection}{0.75em}{}

\setlist[itemize]{leftmargin=1.5em}
\setlist[enumerate]{leftmargin=1.7em}
\renewcommand{\arraystretch}{1.25}

\newcommand{\checkbox}{\(\square\)}
\newcommand{\passbox}{\(\square\) Pass}
\newcommand{\failbox}{\(\square\) Fail}
\newcommand{\blockedbox}{\(\square\) Blocked}

\begin{document}

\begin{titlepage}
  \centering
  \vspace*{1.5cm}
  {\Huge\bfseries\color{eloMaroon} Trial 1 End-to-End System Test Script\par}
  \vspace{0.5cm}
  {\Large Eloquente Catering System\par}
  \vspace{1cm}
  {\large Business-flow rehearsal from staff setup to customer feedback\par}
  \vfill
  \begin{tabular}{>{\bfseries}p{0.28\linewidth}p{0.58\linewidth}}
    Document type & Manual QA and acceptance test script \\
    Test scope & Admin, Customer, Marketing, Accounting, error handling, documents, audit, notifications \\
    Recommended group & Four testers acting as Admin, Customer, Marketing, and Accounting \\
    Date prepared & May 27, 2026 \\
  \end{tabular}
  \vfill
  {\color{eloMuted} Use this packet to record actual outputs, screenshots, defects, and sign-off notes during the trial run.}
\end{titlepage}

\tableofcontents
\newpage

\section{Purpose}
This trial script guides the team through the full business journey: Admin creates staff accounts, a customer discovers the public site, submits a booking, Marketing reviews and prepares the event, Accounting verifies payment, the event is completed, and the customer submits feedback. It also includes skipped features, blocked-action cases, ownership rules, error handling, documents, notifications, and audit checks.

\section{Tester Roles}
\begin{longtable}{p{0.2\linewidth}p{0.72\linewidth}}
\toprule
\textbf{Role} & \textbf{Responsibilities} \\
\midrule
Admin tester & Owner/operator account, staff setup, oversight, settings, audit log, reports, business configuration. \\
Customer tester & Public visitor and registered client; registration, booking, payment, chat, receipt, feedback, account safety. \\
Marketing tester & Booking review, claim ownership, chat, event calendar, preparation, food tasting queue, feedback follow-up. \\
Accounting tester & Payment verification, receipts, ledger, refunds, finance exceptions, accounting dashboard. \\
\bottomrule
\end{longtable}

\section{Ground Rules}
\begin{itemize}
  \item Record pass, fail, or blocked after every case.
  \item Capture screenshots for unexpected behavior, unclear messages, broken layouts, or console/API errors.
  \item Use clear sample data: customer name, event name, event date, pax, package, payment reference, and notes.
  \item When an error is expected, the system should show a clear user-facing message and should not crash.
  \item Do not use real payment credentials unless testing on a proper production or sandbox payment setup.
  \item Do not skip audit checks after sensitive actions such as staff changes, ownership changes, payments, refunds, and document downloads.
\end{itemize}

\section{Result Legend}
\begin{longtable}{p{0.18\linewidth}p{0.75\linewidth}}
\toprule
\textbf{Mark} & \textbf{Meaning} \\
\midrule
\passbox & Behavior matches expected output. \\
\failbox & Behavior is wrong, confusing, insecure, or incomplete. Create a bug entry. \\
\blockedbox & Test could not continue because of missing setup, unavailable dependency, or previous failure. \\
\bottomrule
\end{longtable}

\newpage

\section{Phase 1: Admin Setup}
\subsection{Objective}
Confirm that Admin can access the owner workspace, create staff accounts, enforce first-login password behavior, and audit staff setup actions.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-01 & Admin & Admin logs in & Open login, enter Admin credentials, open Admin dashboard. Try wrong password once. & Admin reaches Admin Console. Wrong password shows a clear error and grants no access. \\
TC-02 & Admin & Create staff accounts & Open People/Staff, create one Marketing and one Accounting account, record generated invite or temporary password. & Staff accounts appear with correct role and account status. Audit records staff creation. \\
TC-03 & Marketing, Accounting & First login and password setup & Log in as each staff user. Complete required password setup if prompted. & Staff cannot enter dashboard until password requirement is satisfied. Correct dashboard loads after completion. \\
TC-04 & Admin & Review audit log & Open Activity Log and filter by account/staff actions. & Entries are business-readable, not route/method/code terms. Sensitive passwords or tokens are not shown. \\
\bottomrule
\end{longtable}

\section{Phase 2: Public Customer Discovery}
\subsection{Objective}
Confirm that public pages are clear, accessible, and route customers toward booking, menu browsing, tasting, and contact inquiry without redundant CTAs.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-05 & Customer & Visit public pages & Open Home, Menu, Packages, Food Tasting, Announcements, and Contact. Check desktop and mobile layout. & Navigation works, CTAs are clear, final CTA is readable, no raw technical text appears. \\
TC-06 & Customer, Marketing & Send contact inquiry & Submit a public inquiry. Marketing checks inquiry queue/notifications. & Customer sees confirmation. Marketing receives a clear inquiry item and can follow up. \\
\bottomrule
\end{longtable}

\section{Phase 3: Customer Registration And Verification}
\subsection{Objective}
Validate account creation, email verification, OTP behavior, and blocked sensitive actions before verification.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-07 & Customer & Register & Create a customer account using valid sample data. Try a duplicate email afterward. & Account is created and verification is requested. Duplicate email is rejected cleanly. \\
TC-08 & Customer & OTP verification & Enter correct OTP, then test expired/wrong/resend behavior if available. & Correct OTP verifies email. Wrong or expired OTP shows a clear message. Resend invalidates older codes. \\
\bottomrule
\end{longtable}

\section{Phase 4: Booking Creation}
\subsection{Objective}
Create a realistic customer booking and confirm it enters the correct review state.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-09 & Customer & Start booking & Start a booking, choose event type/date/package/menu, add pax and venue details, submit. & Booking appears in customer dashboard as submitted for review. Marketing count/claim queue updates. \\
TC-10 & Customer & Update before review & Edit allowed booking details before Marketing approval. & Booking updates are saved, visible to staff, and logged as customer activity. \\
\bottomrule
\end{longtable}

\section{Phase 5: Marketing Claim And Review}
\subsection{Objective}
Confirm explicit ownership: Marketing must claim before mutating a booking, while Admin can override.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-11 & Marketing & View claim queue & Open Booking Reviews, select Claim Queue. & Only unassigned reviewable bookings appear. Completed, cancelled, and owned bookings are excluded. \\
TC-12 & Marketing & Try mutation before claim & From Claim Queue or All Bookings, attempt Ask Details, Approve, or Reject before claiming. & Mutation is blocked with ``Claim this booking before making changes.'' \\
TC-13 & Marketing & Claim booking & Click Claim booking. Refresh the queue. & Booking leaves Claim Queue and appears in My Bookings. Owner label shows current Marketing user. \\
TC-14 & Marketing, Customer & Request customer details & Owner clicks Ask Details. Customer opens dashboard and responds. & Customer sees a clear clarification request. Marketing sees response and can continue review. \\
TC-15 & Marketing & Approve booking & Owner approves booking after details are complete. & Booking becomes approved/confirmed as designed. Customer next step changes to payment or event details. \\
\bottomrule
\end{longtable}

\section{Phase 6: Ownership And Transfer Cases}
\subsection{Objective}
Validate lockout, transfer, acceptance, and release behavior for claimed bookings.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-16 & Marketing B & Non-owner blocked & Marketing B opens All Bookings and tries owner-only actions on Marketing A's booking. & Booking is visible but read-only. Helper says owned by another staff member. \\
TC-17 & Marketing A, Marketing B & Transfer claimed booking & Owner requests transfer to Marketing B. Marketing B accepts or declines in modal. & Pending transfer is visible. Accept changes owner. Decline keeps original owner. Audit records result. \\
TC-18 & Marketing/Admin & Release or unclaim & Owner or Admin releases booking if allowed. & Booking returns to Claim Queue. No mutation happens during release except ownership change. \\
\bottomrule
\end{longtable}

\section{Phase 7: Chat And Collaboration}
\subsection{Objective}
Test booking-aware chat, staff claiming, collaboration, moderation, and resolved/reopened conversations.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-19 & Customer & Start chat & Open Messages, choose booking or General Inquiry, send message. & Conversation appears for staff with client and booking context. \\
TC-20 & Marketing & Claim and reply & Marketing claims conversation and replies. & Customer receives reply. Unassigned chats require claim before staff reply. \\
TC-21 & Marketing/Admin & Collaboration & Owner invites another Marketing user or Admin joins. Collaborator replies. & Collaborator can read/reply but cannot transfer or resolve unless promoted/Admin. \\
TC-22 & Customer, Staff & Edit/delete/reopen & Edit own recent message, soft-delete own message, resolve and reopen conversation. & Time limits and permissions are respected. Deleted message placeholder appears. Audit logs moderation. \\
\bottomrule
\end{longtable}

\section{Phase 8: Payment Flow}
\subsection{Objective}
Confirm customer payment steps, accounting verification, labels, balances, and receipt documents.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-23 & Customer & Open payment step & Open dashboard payment panel and submit proof or use sandbox payment path if configured. & Payment method labels are human-readable. Balance and status are clear. \\
TC-24 & Accounting & Verify payment & Accounting opens Verify Payments, approves or rejects proof, then checks customer dashboard. & Approved payment updates balance and receipt availability. Rejection shows customer-safe reason. \\
TC-25 & Customer, Accounting & Receipt PDF & Download receipt from customer/accounting/admin surfaces. & Branded PDF includes receipt number, booking reference, method label, amount, payment date, balance, and business contact. \\
\bottomrule
\end{longtable}

\section{Phase 9: Event Preparation}
\subsection{Objective}
Validate preparation board visibility, task updates, ownership safety, and prep-list PDF output.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-26 & Marketing & Open preparation board & Open Event Preparation and find the approved event. & Board loads without 500 errors and shows event details, owner, and tasks. \\
TC-27 & Marketing & Update prep tasks & Owner updates task statuses, department, and notes. Non-owner tries the same. & Owner can update. Non-owner is blocked if ownership rules apply. Changes are audited. \\
TC-28 & Marketing & Prep list PDF & Download prep list. & Branded PDF includes schedule, venue, client, pax, menu, dietary notes, equipment, timeline, tasks, owner, and generated timestamp. \\
\bottomrule
\end{longtable}

\section{Phase 10: Event Calendar And Availability}
\subsection{Objective}
Verify calendar month/list views, filters, event stability while switching months, and availability management.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-29 & Marketing & Calendar month view & Open Event Calendar, switch months, open an event. & Events remain visible and do not disappear after month switching. Event drawer opens correctly. \\
TC-30 & Marketing/Admin & Calendar list and filters & Switch to List View. Filter by date, status, event type, venue/city, owner, preparation/payment state. & Filtered rows match month data and show date, event, client, pax, venue, status, owner, and prep state. \\
TC-31 & Admin/Marketing & Date availability & Add or edit date availability/blackout. Customer checks booking date behavior. & Public booking respects availability rules. Audit records availability change. \\
\bottomrule
\end{longtable}

\section{Phase 11: Completion And Event History}
\subsection{Objective}
Confirm completed events leave active queues and appear in shared staff history.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-32 & Marketing/Admin & Mark event completed & Complete event through allowed workflow or run past-submitted cleanup command in a test environment. & Status becomes Completed. Event leaves claim/review/prep active queues. Feedback request is ensured. \\
TC-33 & All staff & Event history notes & Admin, Marketing, and Accounting open Event History and add internal notes. & Completed event appears to all staff. Notes are visible to staff only and do not reopen active workflow. \\
\bottomrule
\end{longtable}

\section{Phase 12: Feedback And Testimonials}
\subsection{Objective}
Validate post-event feedback request, customer submission, low-rating follow-up, and testimonial approval.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-34 & System/Marketing & Feedback request exists & After completion, check customer and staff feedback surfaces. & One feedback request exists. Running completion twice does not create duplicates. \\
TC-35 & Customer & Submit feedback & Customer rates service and optionally allows testimonial use. & Feedback saves successfully and appears in staff review surfaces. \\
TC-36 & Marketing/Admin & Review feedback & Staff updates feedback status, follow-up owner/date, notes, and testimonial approval/rejection. & Public testimonial appears only with customer permission and staff approval. Audit records changes. \\
\bottomrule
\end{longtable}

\section{Phase 13: Refund And Cancellation Cases}
\subsection{Objective}
Exercise refund and cancellation behavior without weakening payment controls.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-37 & Customer, Accounting & Cancellation and refund & Customer requests cancellation if allowed. Accounting/Admin reviews refund path. & Refund queue shows request with original payment method label and clear status. \\
TC-38 & Accounting/Admin & Refund exception & Simulate provider/manual refund failure or mark exception in test data. & Exception appears in Accounting/Admin queues and Next Action panels. Customer-safe messaging is shown. \\
\bottomrule
\end{longtable}

\section{Phase 14: Admin Oversight And Settings}
\subsection{Objective}
Review owner-level oversight, reports, business settings, and staff lifecycle controls.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-39 & Admin & Overview and analytics & Open Admin Overview and Analytics. Check counts, charts, and exception summaries. & Data loads without 500 errors. Completed events are not counted as active review work. \\
TC-40 & Admin & Reports & Generate/download admin reports. & Reports are branded PDFs or properly formatted exports, not raw text or code-like output. \\
TC-41 & Admin & Settings & Update safe business setting in test environment, then verify public/customer effect. & Setting saves, reflects correctly, and audit entry is readable. \\
TC-42 & Admin & Staff lifecycle & Reset password, force password change, deactivate/reactivate staff. Attempt self-deactivation. & Staff lifecycle works. Self-deactivation is blocked. No undefined password crash occurs. \\
\bottomrule
\end{longtable}

\section{Phase 15: Documents, Notifications, And Sounds}
\subsection{Objective}
Validate notification grouping, sound preferences, profile/account safety, and document audit coverage.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-43 & All roles & Notification bell & Trigger booking, payment, chat, feedback, and transfer notifications. & Bell groups unread items by urgency/action/update. Own actions do not create noisy alerts. \\
TC-44 & All roles & Sound preferences & Toggle sound settings and trigger incoming notifications. & Sounds play only after user gesture, respect preferences, and avoid repeated spam. \\
TC-45 & Customer/Staff & Profile and account safety & Update profile, change password, try account deactivation flow where allowed. & Sensitive actions require verification/password confirmation. Operational records remain intact. \\
\bottomrule
\end{longtable}

\section{Phase 16: Final Error Handling Sweep}
\subsection{Objective}
Try predictable failure paths and make sure the app fails gracefully.

\begin{longtable}{p{0.07\linewidth}p{0.13\linewidth}p{0.22\linewidth}p{0.28\linewidth}p{0.22\linewidth}}
\toprule
\textbf{ID} & \textbf{Actor} & \textbf{Test} & \textbf{Steps} & \textbf{Expected Output} \\
\midrule
TC-46 & All roles & Unauthorized access & Try direct URLs for another role's dashboard/API. & Access is denied or redirected safely. No private data leaks. \\
TC-47 & All roles & Invalid inputs & Submit missing fields, bad dates, large text, invalid files, duplicate actions. & User-facing validation appears. No 500 error or broken UI. \\
TC-48 & All roles & Refresh and persistence & Refresh after key state changes, log out/in, revisit pages. & State persists correctly and old links normalize safely. \\
TC-49 & All roles & Mobile/small screen & Test key pages on small viewport. & Primary actions remain visible, text is readable, no controls overlap. \\
TC-50 & Admin/Developer & Production readiness scan & Run build, tests, route list, diff check, and preflight scan. & Automated checks pass or remaining infrastructure items are clearly listed. \\
\bottomrule
\end{longtable}

\newpage

\section{Detailed Execution Notes}
\subsection{Main Business Flow Order}
\begin{enumerate}
  \item Admin logs in and creates Marketing and Accounting staff accounts.
  \item Staff users complete first-login/password setup.
  \item Customer explores public pages, registers, verifies email, and creates a booking.
  \item Marketing confirms the booking appears in Claim Queue.
  \item Marketing verifies unclaimed bookings cannot be mutated, then explicitly claims the booking.
  \item Marketing requests clarification if needed, receives the customer response, and approves the booking.
  \item Customer completes payment step.
  \item Accounting verifies payment and checks receipt output.
  \item Marketing updates preparation tasks and downloads the prep list.
  \item Staff checks event calendar and availability behavior.
  \item Event is completed and appears in shared Event History.
  \item Customer submits feedback.
  \item Marketing/Admin reviews feedback and testimonial eligibility.
  \item Admin reviews reports, settings, audit entries, and staff lifecycle controls.
\end{enumerate}

\subsection{Error Handling To Try During The Flow}
\begin{itemize}
  \item Wrong password and invalid OTP.
  \item Duplicate registration email.
  \item Booking form with missing required fields.
  \item Marketing mutation before claim.
  \item Non-owner mutation after another staff member claims a booking.
  \item Duplicate claim after a booking was already claimed.
  \item Payment proof rejection.
  \item Direct URL access to another role's dashboard.
  \item Expired or old links such as old dashboard query parameters.
  \item Refresh during or after state changes.
\end{itemize}

\subsection{Documents To Inspect}
\begin{itemize}
  \item Customer receipt/payment receipt.
  \item Booking summary/customer copy, if available.
  \item Event preparation list.
  \item Calendar report.
  \item Admin reports.
  \item Refund/payment documentation.
\end{itemize}

\subsection{Audit Actions To Confirm}
\begin{itemize}
  \item Login, failed login, password reset, forced password change.
  \item Staff creation, role change, deactivation, reactivation.
  \item Booking claim, release, transfer request, accept, decline.
  \item Booking approval, rejection, clarification request, status changes.
  \item Chat claim, join, collaborator changes, resolve, reopen, message moderation.
  \item Payment proof upload, verification, rejection, refund actions.
  \item Feedback follow-up, testimonial approval/rejection, event history note.
  \item Document generation/download.
  \item Settings, menu, package, announcement, availability, and preview actions.
\end{itemize}

\newpage

\section{Trial Result Template}
\subsection{Pass/Fail Summary}
\begin{longtable}{p{0.24\linewidth}p{0.16\linewidth}p{0.16\linewidth}p{0.16\linewidth}p{0.2\linewidth}}
\toprule
\textbf{Area} & \textbf{Passed} & \textbf{Failed} & \textbf{Blocked} & \textbf{Notes} \\
\midrule
Admin & & & & \\
Customer & & & & \\
Marketing & & & & \\
Accounting & & & & \\
Cross-role flow & & & & \\
Documents/PDFs & & & & \\
Audit/notifications & & & & \\
Error handling & & & & \\
\bottomrule
\end{longtable}

\subsection{Bug Log}
\begin{longtable}{p{0.08\linewidth}p{0.15\linewidth}p{0.22\linewidth}p{0.22\linewidth}p{0.12\linewidth}p{0.12\linewidth}}
\toprule
\textbf{No.} & \textbf{Case ID} & \textbf{Issue} & \textbf{Expected Behavior} & \textbf{Severity} & \textbf{Owner} \\
\midrule
1 & & & & & \\
2 & & & & & \\
3 & & & & & \\
4 & & & & & \\
5 & & & & & \\
\bottomrule
\end{longtable}

\subsection{Business Flow Verdict}
\begin{itemize}
  \item \checkbox\ The complete business flow can be performed without developer assistance.
  \item \checkbox\ Each role understands what to do next.
  \item \checkbox\ Ownership and permission rules behave correctly.
  \item \checkbox\ Customer-facing copy is understandable.
  \item \checkbox\ Staff-facing audit logs are business-readable.
  \item \checkbox\ PDFs and exports are branded and complete.
  \item \checkbox\ No critical 500 errors or broken screens remain.
  \item \checkbox\ Remaining issues are minor and documented.
\end{itemize}

\vspace{1cm}
\begin{longtable}{p{0.3\linewidth}p{0.3\linewidth}p{0.3\linewidth}}
\toprule
\textbf{Tester} & \textbf{Role} & \textbf{Signature / Date} \\
\midrule
 & Admin & \\
 & Customer & \\
 & Marketing & \\
 & Accounting & \\
\bottomrule
\end{longtable}

\end{document}
